Model Recognition as Planning

### 2018-11-16 doc/icaps-19/model-recognition.tex
added related work section to icaps19 paper

\section{Related work}
\label{sec:related}
An intriguing research line related with {\em model recognition} is {\em model reconciliation}~\cite{ChakrabortiSZK17} where model edition is used to conform the PDDL models of two different agents wrt an observation of a plan execution. In {\em model recognition} we also conform every input model $\mathcal{M}$ in the $M$ set with another model $\mathcal{M}'$ s.t. it is consistent with the input observation. Note however that in the {\em model recognition} task, the model $\mathcal{M}'$ is not given as input but instead, this model $\mathcal{M}'$ is computed for every $\mathcal{M}\in M$. Further, {\em model recognition as planning} shows that two input planning models can be conformed using an off-the-shelf classical planner and wrt an observation of a planning execution that contains no information of the applied actions.

>>>>

\section{Related work}
\label{sec:related}
An intriguing research line related with {\em model recognition} is {\em model reconciliation}~\cite{ChakrabortiSZK17} where model edition is used to conform the PDDL models of two different agents (or the model of an agent with an {\em annotated model}~\cite{sreedharan2018handling}) wrt an observation of a plan execution. In {\em model recognition} we also conform every input model $\mathcal{M}$ in the $M$ set with another model $\mathcal{M}'$ s.t. it is consistent with the input observation. Note however that in the {\em model recognition} task, the model $\mathcal{M}'$ is not given as input but instead, this model $\mathcal{M}'$ is computed for every $\mathcal{M}\in M$. Further, {\em model recognition as planning} shows that two input planning models can be conformed using an off-the-shelf classical planner and wrt an observation of a planning execution that contains no information of the applied actions.
